TODO: A Survey of StarCraft AI Techniques

### 2012-05-04 survey.tex
added a ref + beginning cleaning

\subsection{Perception}
Every AI needs to observe the world in order to analyze it and take decisions. In RTS games this task isn't trivial since we have to deal with imperfect information.

\textbf{Spatial}

Terrain analysis supplies the AI with chunks of abstract information about the map in order to help in making decisions. This analysis is usually performed off-line, in order to save processing time during gameplay.

Pottinger \cite{Pottinger00} described \emph{BANG!} engine implemented by Ensemble Studios for the game Age of Empires 2. This engine provides terrain analysis functionalities to the game using influence maps and areas with connectivity information. Later works \cite{Forbus01} showed the importance to have qualitative spatial information, and some others \cite{Karavelas04}\cite{Hale08} focused on spatial decomposition. The most recent work \cite{Perkins10} presented an algorithm using Voronoi diagrams to detect regions and relevant choke points.

\textbf{Temporal}

In \cite{WeberAIIDE11} a particle model is used to tracks opponent units under fog of war over time.

{\color{ForestGreen}
Anyone did anything here? I think only Skynet uses temporal reasoning...
Maybe heat maps?? but I can't find any reference...
}

\textbf{Enemy}

Opponent modeling is the process of keeping track of what the enemy is doing during a game in order to estimate the probability of it using a specific strategy.

@@

\textbf{Ally}

{\color{ForestGreen}
Anyone did anything here?
}

>>>>

\subsection{Perception}
XXX Every AI needs to observe the world in order to analyze it and take decisions. In RTS games this task isn't trivial since we have to deal with imperfect information.

%\textbf{Spatial}

XXX Terrain analysis supplies the AI with chunks of abstract information about the map in order to help in making decisions. This analysis is usually performed off-line, in order to save processing time during gameplay.

Pottinger \cite{Pottinger00} described \emph{BANG!} engine implemented by Ensemble Studios for the game Age of Empires II. This engine provides terrain analysis functionalities to the game using influence maps and areas with connectivity information.

\cite{Forbus2002} showed the importance to have qualitative spatial informationfor wargames, for which they used geometric and pathfinding analysis.

\cite{Hale08} presented a 2D geometric navigation mesh generation method from expanding convex regions from seeds.

\cite{Perkins10} applied Voronoi decomposition (then pruning) %\cite{Karavelas04}
to detect regions and relevant choke points in RTS maps. This approach is implemented for StarCraft in BWTA\footnote{\url{http://code.google.com/p/bwta/}}.

%\textbf{Temporal}
% Isla 2006 Game AI Programming Wisdom 3. Charles River Media. chapter Probabilistic Target Tracking and Search Using Occupancy Maps, 379–388. ?

\cite{Hladky2008} benchmarked hidden semi-Markov models (HSMM) and particle filters in FPS units tracking. They showed that the accuracy of occupancy maps was improved using movement models (learned from the player behavior) in HSMM. 
% comparable with human experts ?

\cite{HagelbackJ08} presented a multi-agent potential fields based bot able to deal with fog of war in Tankbattle. XXX

\cite{WeberAIIDE11} used a particle model, with a simple linear trajectory update, to track opponent units under fog of war in StarCraft.

% {\color{ForestGreen}
% Anyone did anything here? I think only Skynet uses temporal reasoning...
% Maybe heat maps?? but I can't find any reference...
% }

%\textbf{Enemy}

XXX Opponent modeling is the process of keeping track of what the enemy is doing during a game in order to estimate the probability of it using a specific strategy.

@@

% \textbf{Ally}
% 
% {\color{ForestGreen}
% Anyone did anything here?
% }
